---
title: "NYC TAXI EDA"
output: html_notebook
---



```{r}
# Define multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```
# 1.2 LOAD DATA
```{r}
train <- as.tibble(fread('train.csv'))
test <- as.tibble(fread('test.csv'))
# sample_submit <- as.tibble(fread('sample_submission.csv'))
```

# 1.3 DATA SET STRUCTURE
We find : 

* vendor id only takes two values(1 or 2), presumably two different taxi company 
* pickup_datetime needs to be re-formatted into a more useful shape 
* passenger_count vary from 1 to 9 
* pickup/dropoff longitude,latitude - coordinate that meter was activated/deactivated
* store_and_fw_flag - trip data is held in memory or sent immediately (y/n) 
* trip_duration - target variable 
```{r}
# test 
summary(train)
glimpse(train)

#train 
summary(test)
glimpse(test)
```


# 1.4 MISSING VALUES 
* no missing value 
```{r}
sum(is.na(train))
sum(is.na(test))
```


# 1.5 COMBINING TRAIN AND TEST 
* combine two data sets into one to preprocess 
```{r}
combine = bind_rows(train %>% mutate(dset="train"),
                    test %>% mutate(dset="test",
                                    dropoff_datetime=NA,
                                    trip_duration=NA))

combine <- combine %>% mutate(dset = factor(dset))

```

# 1.6 REFORMATING FEATURES 
* turning the data and time from characters into date objects 
* vendor_id as a factor (easy to visualize relationship with other features)
* test? 
```{r}
train = train %>%
  mutate(pickup_datetime = ymd_hms(pickup_datetime),
         dropoff_datetime = ymd_hms(dropoff_datetime),
         vendor_id = factor(vendor_id),
         passenger_count = factor(passenger_count))
```



# 2.INDIVISUAL FEATURE VISUALIZATION 
각 변수의 분포를 우선 살펴본다 

pickup/dropoff coordinates

* manhattan only, JFK is another notable hotspot
```{r}
set.seed(1234)
foo <- sample_n(train, 8e3)

leaflet(data = foo) %>% addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircleMarkers(~ pickup_longitude, ~pickup_latitude, radius = 1,
                   color = "blue", fillOpacity = 0.3)

leaflet(data = foo) %>% addProviderTiles("Esri.NatGeoWorldMap") %>%
  addCircleMarkers(~ dropoff_longitude, ~dropoff_latitude, radius = 1,
                   color = "blue", fillOpacity = 0.3)

```

trip_duration

* log-normal with a peak of 1000 seconds (27min)
* several short rides less than 10 sec
```{r}
train %>%
  ggplot(aes(trip_duration)) +
  geom_histogram(fill = "red", bins = 150) + 
  scale_x_log10() +
  scale_y_sqrt()
```

* tail data
```{r}
train %>%
  arrange(desc(trip_duration)) %>%
  select(trip_duration, pickup_datetime, dropoff_datetime, everything()) %>%
  head(10)
```

* homogeneous, covering between January and Jul
* drop around late January - weather 
```{r}
# View(train)
p1 <- train %>%
  ggplot(aes(pickup_datetime)) +
  geom_histogram(fill = "red", bins = 120) +
  labs(x = "Pickup dates")

p2 <- train %>%
  ggplot(aes(dropoff_datetime)) +
  geom_histogram(fill = "blue", bins = 120) +
  labs(x = "Dropoff dates")

layout <- matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p1, p2, layout=layout)
```
```{r}
train %>%
  group_by(passenger_count) %>%
  count()
```

```{r}
p1 <- train %>%
  group_by(passenger_count) %>%
  count() %>%
  ggplot(aes(passenger_count, n, fill = passenger_count)) +
  geom_col() +
  scale_y_sqrt() +
  theme(legend.position = "none")

p2 <- train %>%
  ggplot(aes(vendor_id, fill = vendor_id)) +
  geom_bar() +
  theme(legend.position = "none")

p3 <- train %>%
  ggplot(aes(store_and_fwd_flag)) +
  geom_bar() +
  theme(legend.position = "none") +
  scale_y_log10()

p4 <- train %>%
  mutate(wday = wday(pickup_datetime, label = TRUE)) %>%
  group_by(wday, vendor_id) %>%
  count() %>%
  ggplot(aes(wday, n, colour = vendor_id)) +
  geom_point(size = 4) +
  labs(x = "Day of the week", y = "Total number of pickups") +
  theme(legend.position = "none")

p5 <- train %>%
  mutate(hpick = hour(pickup_datetime)) %>%
  group_by(hpick, vendor_id) %>%
  count() %>%
  ggplot(aes(hpick, n, color = vendor_id)) +
  geom_point(size = 4) +
  labs(x = "Hour of the day", y = "Total number of pickups") +
  theme(legend.position = "none")

layout <- matrix(c(1,2,3,4,5,5),3,2,byrow=TRUE)
multiplot(p1, p2, p3, p4, p5, layout=layout)
```
* a few trips with zero, or seven to nine passengers
* The vast majority of rides had only a single passenger
* Vendor 2 has significantly more trips in this data set than vendor 1
* monday : quiest / friday : busiest
* dip during morning and 4pm

```{r}
p1 <- train %>%
  mutate(hpick = hour(pickup_datetime),
         Month = factor(month(pickup_datetime, label = TRUE))) %>%
  group_by(hpick, Month) %>%
  count() %>%
  ggplot(aes(hpick, n, color = Month)) +
  geom_line(size = 1.5) +
  labs(x = "Hour of the day", y = "count")

p2 <- train %>%
  mutate(hpick = hour(pickup_datetime),
         wday = factor(wday(pickup_datetime, label = TRUE))) %>%
  group_by(hpick, wday) %>%
  count() %>%
  ggplot(aes(hpick, n, color = wday)) +
  geom_line(size = 1.5) +
  labs(x = "Hour of the day", y = "count")

layout <- matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p1, p2, layout=layout)
```
* January and June have fewer trips, whereas March and April are busier months
* The weekend (Sat and Sun, plus Fri to an extend) have higher trip numbers during the early morning ours but lower ones in the morning between 5 and 10

# 3.FEATURE RELATIONS 
3.1 Pickup date/time vs trip_duration
```{r}
p1 <- train %>%
  mutate(wday = wday(pickup_datetime, label = TRUE)) %>%
  group_by(wday, vendor_id) %>%
  summarise(median_duration = median(trip_duration)/60) %>%
  ggplot(aes(wday, median_duration, color = vendor_id)) +
  geom_point(size = 4) +
  labs(x = "Day of the week", y = "Median trip duration [min]")

p2 <- train %>%
  mutate(hpick = hour(pickup_datetime)) %>%
  group_by(hpick, vendor_id) %>%
  summarise(median_duration = median(trip_duration)/60) %>%
  ggplot(aes(hpick, median_duration, color = vendor_id)) +
  geom_smooth(method = "loess", span = 1/2) +
  geom_point(size = 4) +
  labs(x = "Hour of the day", y = "Median trip duration [min]") +
  theme(legend.position = "none")

layout <- matrix(c(1,2),2,1,byrow=FALSE)
multiplot(p1, p2, layout=layout)
```
* Vendor 2, the one with the more frequent trips, also has consistently higher trip durations
* a peak in the early afternoon and dips around 5-6am and 8pm.


3.2 Passenger count and Vendor vs trip_duration

```{r}
train %>%
  ggplot(aes(passenger_count, trip_duration, color = passenger_count)) +
  geom_boxplot() +
  scale_y_log10() +
  theme(legend.position = "none") +
  facet_wrap(~ vendor_id) +
  labs(y = "Trip duration [s]", x = "Number of passengers")
```
* Between 1 and 6 passengers the median trip durations are remarkably similar

```{r}
train %>%
  ggplot(aes(trip_duration, fill = vendor_id)) +
  geom_density(position = "stack") +
  scale_x_log10()
```
```{r}
train %>%
  group_by(vendor_id) %>%
  summarise(mean_duration = mean(trip_duration),
            median_duration = median(trip_duration))
```
* the medians are very similar, whereas the means are likely skewed by vendor 2 containing most of the long-duration outliers





















